---
title: "realtorio final 2018"
author: "Emilia Brasilio"
date: "21 de novembro de 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Sistema de medida de fluxos - média 10 min
|coletas|periodo     | falhas   |id logger| Net|
|-------|------------|----------|---------|-----
|31616  | inicio     |          |60972
|10817  | fim - sonico com ptoblema
|13717  |16Mai19:00 - 19Mai02:30|52356    |
|15117  |19Mai15:30 - 01Jun05:00|52356    |
|20117  |17Jun20:00 - 21Jul10:00|52356    |
|24117  |14Ago16:30 - 31Ago06:00|52356    |
|26017  |31Ago11:30 - 19Set15:00|52356    |
|30017  |01Out03:50 - 10Nov16:20|52356    |
|34517  |                       |52356  TEM SIM PROCESSAR  |
|03118  |24Dez17:40 - 01Fev10:00|52356    |
|05818  |01Fev10:20 - 28Fev17:10|52356    |
|08618  |28Fev17:50 - 28Mar13:00|52356    |
|14918  |28Mar13:20 - 03Mai17:10|52356    |
|16318  | Não houve coleta      |52356  TEM SIM PROCESSAR   |
|20018  |10Jun09:30 - 19Jul14:00|52356    |
|23018  |19Jul14:20 - 16Ago17:20|52356    |
|26818  |17Ago21:40 - 25Set17:00|52356    | 16 à 20/08 sem dados, arquivo ok





```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
